### 2015-10-26 analysis/index.Rmd

*  [Illustrate Zero Assumption](makefig_FDReg.html)
*  [Illustatrate dilution effect of low-precision observations](make_GOODPOOR_figs.html)

>>>>

*  [Illustrate Zero Assumption](makefig_FDReg.html)
*  [Illustatrate dilution effect of low-precision observations](make_GOODPOOR_figs.html)
*  [Adpative Shrinkage](adaptive_shrinkage.html)

### 2015-10-26 analysis/plot_cdf_eg.Rmd

```{r egcdf}
#pdf("../paper/figures/egcdf.pdf",height=3,width=9)
plot_mean_cdf(1)
```

```{r mean_cdf}
#pdf("../paper/figures/mean_cdf.pdf",height=3,width=9)
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n","ash.u","ash.hu","truth"),pi0filter=TRUE)
```

```{r mean_cdf_nopen}
#pdf("../paper/figures/mean_cdf_nopen.pdf",height=3,width=9)
names(myColors) <- c("mixfdr.tnull","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr","truth")
colScale <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n.s","ash.u.s","ash.hu.s","truth"),pi0filter=TRUE)
```

>>>>

```{r egcdf, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
#pdf("../paper/figures/egcdf.pdf",height=3,width=9)
plot_mean_cdf(1)
```

```{r mean_cdf, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
#pdf("../paper/figures/mean_cdf.pdf",height=3,width=9)
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n","ash.u","ash.hu","truth"),pi0filter=TRUE)
```

```{r mean_cdf_nopen, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
#pdf("../paper/figures/mean_cdf_nopen.pdf",height=3,width=9)
names(myColors) <- c("mixfdr.tnull","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr","truth")
colScale <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n.s","ash.u.s","ash.hu.s","truth"),pi0filter=TRUE)
```

### 2015-10-26 analysis/plot_egdens.Rmd

```{r scenario_density}
#pdf(PLOTFILE,height=3,width=9)
ggplot(df, aes(x=x,y=y)) + geom_line(size=1.2,linetype=1) + facet_grid(.~scenario) + ylab("density")
#dev.off()
```

>>>>

```{r scenario_density, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
#pdf(PLOTFILE,height=3,width=9)
ggplot(df, aes(x=x,y=y)) + geom_line(size=1.2,linetype=1) + facet_grid(.~scenario) + ylab("density")
#dev.off()
```

### 2015-10-26 paper/main.tex

\begin{figure}[h!] 
\begin{subfigure}{\textwidth}
	\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/egcdf-1.png}
	\caption{Example estimated cdfs for single data sets compared with truth. The unimodal assumption made by the ash methods effectively regularizes estimates compared with \mixfdr.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/mean_cdf-1.png}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here use penalty (\ref{eqn:penalty}) so $\pi_0$ is systematically overestimated.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/mean_cdf_nopen-1.png}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here do not use penalty (\ref{eqn:penalty}) so $\pi_0$ is not systematically overestimated. Systematic differences from the truth in ``skew" and ``bimodal" scenarios highlight the effects of model mis-specification.}
\end{subfigure}
\caption{Comparisons of estimated cdfs of $g$ and true cdf of $g$. See Figure \ref{fig:pi0sims} for simulation scenarios.} \label{fig:egcdf}
\end{figure}

>>>>

\begin{figure}[h!] 
\begin{subfigure}{\textwidth}
	\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/egcdf-1.pdf}
	\caption{Example estimated cdfs for single data sets compared with truth. The unimodal assumption made by the ash methods effectively regularizes estimates compared with \mixfdr.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/mean_cdf-1.pdf}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here use penalty (\ref{eqn:penalty}) so $\pi_0$ is systematically overestimated.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/mean_cdf_nopen-1.pdf}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here do not use penalty (\ref{eqn:penalty}) so $\pi_0$ is not systematically overestimated. Systematic differences from the truth in ``skew" and ``bimodal" scenarios highlight the effects of model mis-specification.}
\end{subfigure}
\caption{Comparisons of estimated cdfs of $g$ and true cdf of $g$. See Figure \ref{fig:pi0sims} for simulation scenarios.} \label{fig:egcdf}
\end{figure}
